---
title: "Maize root bacteria isolates phylogeny"
author: "Lisa Thönen"
date: "March 2023"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,include=FALSE}
rm(list=ls())
```

```{r,include=FALSE}
# install.packages("dplyr")
# install.packages("plyr")
# install.packages("magrittr")
# install.packages("ggplot2")
# install.packages("readxl")
# install.packages("tidyr")
# install.packages("readr")
# install.packages("stringr")
# install.packages("ggplot2")
# install.packages("forcats")
# install.packages("ggpmisc")
# install.packages("pander")
# install.packages("tidyr")
# install.packages("tibble")
# install.packages("RColorBrewer")
# install.packages("pheatmap")
# install.packages("ggdendro")
# install.packages("reshape2")
# install.packages("grid")
# install.packages("ape")
# install.packages("ggtree")
# install.packages("aplot")
# install.packages("wesanderson")
# install.packages("ggsci")
# install.packages("ggnewscale")
# install.packages("data.tree")
# install.packages("networkD3")
# install.packages("Cairo")

# install.packages("ggtreeExtra")
# install.packages("treeio")
# 
# install.packages(pckgs)

# ggtree package

# if (!requireNamespace("BiocManager", quietly = TRUE))
#      install.packages("BiocManager")
# 
# BiocManager::install("ggtree")

# BiocManager::install("ggtreeExtra")
```

```{r, include=FALSE}
library(plyr) # please load plyr first, then dplyr
library(dplyr)
library(magrittr)
library(ggplot2)
library(readxl)
library(tidyr)
library(readr)
library(stringr)
library(ggplot2)
library(forcats)
library(ggpmisc)
library(pander)
library(tidyr)
library(tibble)
library(RColorBrewer)
library(pheatmap)
library(ggdendro)
library(reshape2)
library(grid)
library(ape)
library(ggtree)
# library(aplot)
library(wesanderson)
library(ggsci)
library(ggnewscale)
library(data.tree)
library(networkD3)
library(Cairo)
# library(ggtreeExtra)
# library(treeio)
```


# Load and format input data
Input: *Metadata bacteria:* Database_MRB_isolates & database_raw, *Mapping results:* Mapping in 4 soils and feedback, *Phylogeny:* Tree compouted from 16s sequences

```{r, warning=FALSE, include=FALSE}
sequences <- read_excel("./Input/190313_SynCom_tree_sequences.xlsx")
database_raw <- read_excel("./Input/__Database_MRB_isolates_sequences.xlsx")
Database_MRB_isolates <- read.csv("./Input/Database_MRB_isolates.csv")
Database_MRB_isolates %<>% dplyr::select(Strain, Strain_old.x) 
```

```{r, warning=FALSE, include=FALSE}
database_raw <- left_join(database_raw, Database_MRB_isolates, by = "Strain")
database_raw <- database_raw %>% dplyr::select(-Strain_old.x)
```

```{r, warning=FALSE, include=FALSE}
### Newick tree ###
Tree_16s_unique <- 
   ggtree::read.tree("./Input/220427_Tree_Marco_RAxML_bipartitionsBranchLabels.concatenated_rooted")

# Tree_16s_unique <- phytools::read.newick("../220427_Tree_Marco_RAxML_bipartitionsBranchLabels.concatenated_rooted")

Tree_16s_unique$tip.label <- gsub("_1492r","", Tree_16s_unique$tip.label)
Tree_16s_unique$tip.label <- gsub("_27f","", Tree_16s_unique$tip.label)
```

```{r, warning=FALSE, include=FALSE}
Mapping4soils <- read_rds("./Input/all_phy_psmelt_iso_BX_abundance_cum.rds")

Mapping4soils_mean_abundance_ASV_cum <- Mapping4soils

HuFeedback <- read_rds("./Input/all_phy_psmelt_FB_BXp_iso_new_mapping_cum_abun.rds")

HuFeedback_mean_abundance <- HuFeedback

HuFeedback_Mapping4soils <- rbind(HuFeedback_mean_abundance %>% mutate(compartment = "root") %>% mutate(location = "Greenhouse") %>% mutate(background = "B73") %>% mutate(exp = "feedback"), Mapping4soils_mean_abundance_ASV_cum %>% mutate(exp = "field") %>%  filter(compartment %in% "root"))

Mapping_4soils_Hu <- HuFeedback_Mapping4soils %>% mutate(location_background_exp = interaction(location, background, exp, sep = "_")) %>% as.data.frame() %>%  dplyr::select(-location, -background, -exp, -compartment)  %>% unique() %>% group_by(Strain, location_background_exp) %>% pivot_wider(names_from = location_background_exp, values_from = Abundance_cum_Strain)
```

```{r, warning=FALSE, include=FALSE}
database <- left_join(database_raw, Mapping_4soils_Hu, by = "Strain") %>% unique()
```

```{r, warning=FALSE, include=FALSE}
database$Primer_rv <- gsub("NA", "27f", database$Primer_rv)
database$Isolation_media <- gsub("TSB_MBOA_fridge", "TSB_MBOA", database$Isolation_media)
database$Isolation_media <- gsub("TSB_MBOA_species", "TSB_MBOA", database$Isolation_media)
database$Isolation_media <- gsub("TSB_MBOA_compartment", "TSB_MBOA", database$Isolation_media)
database$Isolation_media <- gsub("TSB_full_Katja", "TSB_MBOA", database$Isolation_media)
database$Isolation_media <- gsub("Strep", "Flour", database$Isolation_media)
database$Isolation_media <- gsub("Rif", "PseudoA", database$Isolation_media)
```

```{r, warning=FALSE, include=FALSE}
database$Plant <- gsub("B73_WT_root", "B73_WT", database$Plant)
database$Plant <- gsub("B73_WT_RoRh", "B73_WT", database$Plant)
database$Plant <- gsub("B73_WT_rhizo", "B73_WT", database$Plant)
database$Plant <- gsub("B73_bx_rhizo", "B73_bx1", database$Plant)
database$Plant <- gsub("B73_bx_root", "B73_bx1", database$Plant)
database$Plant <- gsub("B73_WT_soil", "soil", database$Plant)
database$Plant <- gsub("B73_bx_soil", "soil", database$Plant)

database$Plant <- factor(database$Plant, levels=c("B73_WT",  "B73_bx1",  "wheat",  "medicago", "brassica", "arabidopsis", "soil"))
```

```{r, warning=FALSE, include=FALSE}
database$Genome <- gsub("NA", "no", database$Genome)
database$Genome <- gsub("Bern", "yes", database$Genome)
database$Genome <- gsub("Spain", "yes", database$Genome)
database$Genome <- gsub("Zurich", "yes", database$Genome)
```

```{r, warning=FALSE, include=FALSE}
database$Genus <- gsub("Allorhizobium-Neorhizobium-Pararhizobium-Rhizobium", "Rhizobium", database$Genus)
database$Genus <- gsub("Micrococcineae", "Microbacterium", database$Genus)
database$Phylum <- gsub("Deinococcota", "Deinococcus-Thermus", database$Phylum)
database$Phylum <- gsub("Actinobacteriota", "Actinobacteria", database$Phylum)
database$Phylum <- gsub("Bacteroidota", "Bacteroidetes", database$Phylum)
```

```{r, warning=FALSE, include=FALSE}
# Assignment of colours plant

database$cols <- as.character(database$Plant)
database[database$Plant == "B73_WT", ]$cols <- "gold" 
database[database$Plant == "B73_bx1", ]$cols <- "forestgreen" 
database[database$Plant == "wheat", ]$cols <- "tan3" 
database[database$Plant == "medicago", ]$cols <- "salmon4"
database[database$Plant == "brassica", ]$cols <- "khaki4" 
database[database$Plant == "arabidopsis", ]$cols <- "khaki3" 
database[database$Plant == "soil", ]$cols <-  "wheat" 

## collapsed color vector for each level
temp <- data.frame(database$Plant, database$cols)
temp <- plyr::ddply(temp, .variables="database.Plant", .fun=unique)   
level_cols_plants <- as.character(temp[,2])
names(level_cols_plants) <- temp[,1]
```

```{r, warning=FALSE, include=FALSE}
# Assignment of colours families

database$cols_Family <- as.character(database$Family)
database$Family <- gsub("Chitinophagales", "Chitinophagaceae", database$Family)
database$Family <- gsub("Pseudomonadales", "Pseudomonadaceae", database$Family)
database[database$Family=="Bacillaceae" , ]$cols_Family <- "#004586"
database[database$Family=="Chitinophagaceae" , ]$cols_Family <- "#ff420e"
database[database$Family=="Enterobacteriaceae" , ]$cols_Family <- "#ffd320"
database[database$Family=="Erwiniaceae" , ]$cols_Family <- "#579d1c"
database[database$Family=="Microbacteriaceae" , ]$cols_Family <- "#7e0021"
database[database$Family=="Micrococcaceae" , ]$cols_Family <- "#83caff"
database[database$Family=="Nocardioidaceae" , ]$cols_Family <- "#314004"
database[database$Family=="Oxalobacteraceae" , ]$cols_Family <- "#aecf00"
database[database$Family=="Pseudomonadaceae" , ]$cols_Family <- "#4b1f6f"
database[database$Family=="Rhizobiaceae", ]$cols_Family <- "#ff950e"
database[database$Family=="Sphingomonadaceae", ]$cols_Family <- "#c5000b"
database[database$Family=="Xanthomonadaceae", ]$cols_Family <- "#0084d1"
database[database$Family=="Streptomycetaceae" , ]$cols_Family <- "#8b995a"
database[database$Family=="Flavobacteriaceae" , ]$cols_Family <- "#F0D5B4"
database[database$Family=="Paenibacillaceae" , ]$cols_Family <- "#8f9ec9"
database[database$Family=="Planococcaceae", ]$cols_Family <- "#7F5757"
database[database$Family=="Moraxellaceae", ]$cols_Family <- "#a73e62"
database[database$Family=="Sphingobacteriaceae", ]$cols_Family <- "#c75536"
database[database$Family=="Deinococcaceae", ]$cols_Family <- "#031e33"
database[database$Family=="Weeksellaceae", ]$cols_Family <- "grey"

## collapsed color vector for each level
temp <- data.frame(database$Family, database$cols_Family)
temp <- plyr::ddply(temp, .variables="database.cols_Family", .fun=unique)   
database_level_cols_Family <- as.character(temp[,2])
names(database_level_cols_Family) <- temp[,1]
```

```{r, warning=FALSE, include=FALSE}
# Assignment of colours phylum

database$cols_Phylum <- as.character(database$Phylum)
database[database$Phylum=="Firmicutes" , ]$cols_Phylum <- "#004586" 
database[database$Phylum=="Proteobacteria" , ]$cols_Phylum <- "#7e0021"
database[database$Phylum=="Actinobacteria" , ]$cols_Phylum <- "#579d1c"
database[database$Phylum=="Bacteroidetes" , ]$cols_Phylum <- "#ffd320" 
database[database$Phylum=="Deinococcus-Thermus" , ]$cols_Phylum <- "#ff950e"

## collapsed color vector for each level
temp <- data.frame(database$Phylum, database$cols_Phylum)
temp <- plyr::ddply(temp, .variables="database.cols_Phylum", .fun=unique)   
database_level_cols_Phylum <- as.character(temp[,2])
names(database_level_cols_Phylum) <- temp[,1]
```

# Phylogeny 
Phylogeny without tree using radialNetwork()
```{r, warning=FALSE, error = FALSE, echo=FALSE, message=FALSE, fig.width=10, fig.height=7.5}
database %>% 
  dplyr::select(Phylum, Family, Genus, Strain) %>% 
  na.omit() %>% 
  filter(!Phylum %in% "NA") %>% 
  mutate(pathString = paste(Phylum, Family, Genus, Strain, sep = "/")) %>%
  as.data.frame() %>% 
  as.Node() %>% 
  ToListExplicit(.,unname = TRUE) %>% 
  radialNetwork(fontSize=15)
```


```{r, warning=FALSE, include=FALSE}
# Phylogeny with tree (Newick tree)

ptree <- Tree_16s_unique %>%
  ggtree(aes(x =0.1), branch.length = "none", ladderize = FALSE, layout = "circular") +
    geom_tiplab(size=3)

ptree
```

```{r, warning=FALSE, include=FALSE}
# join metadata to the tree

tree_data <- database %>% mutate(id = str_c(Genus, Strain, sep ="_")) 

MBOA_tolerance_MRB <- read.csv("./Input/all_MBOA_tolerance_MRB.csv")
MBOA_tolerance_MRB %<>% mutate(tolerance_test = "TRUE")

tree_data <- left_join(tree_data, MBOA_tolerance_MRB, by = "Strain")

# filter strains in tree
strains_tree <- Tree_16s_unique$tip.label %>% unique() 
database_raw %>% filter(!Strain %in% strains_tree) %>% unique() 
```

# Trees
```{r, warning = FALSE, error = FALSE, echo=FALSE, message=FALSE, fig.width=15, fig.height=12}
database_Strain_Family <- database %>% dplyr::select(Strain, Family) %>% filter(Strain %in% strains_tree)

tree_shading_family_branch_line <- ggtree::ggtree(Tree_16s_unique, branch.length = "branch.length", layout = "circular") %<+% database_Strain_Family +
   geom_tippoint(aes(color = Family), size = 2) 
 # geom_tiplab(align = TRUE) 
#   linesize = 0.5,
#   geom = "text",
#   offset = 0,
#   as_ylab = FALSE) +
#   geom_treescale(x=0.7, y=-1.1, fontsize=3, linesize=1, offset=1)+
  # geom_highlight(node=204, fill='grey80', alpha=0.6, extendto=1)+
  # geom_highlight(node=155, fill='grey80', alpha=0.6, extendto=1)+
  # geom_highlight(node=225, fill='grey10', alpha=0.6, extendto=1)+
  # geom_highlight(node=247, fill='grey40', alpha=0.6, extendto=1)+
  # scale_color_manual(values = database_level_cols_Family)

tree_shading_family_branch_line
```

```{r, warning = FALSE, error = FALSE, echo=FALSE, message=FALSE, fig.width=15, fig.height=12}
database_Strain_Family <- database %>% dplyr::select(Strain, Family)

tree_family_branch_line <- ggtree::ggtree(Tree_16s_unique, branch.length = "branch.length", ladderize = TRUE, layout = "circular") %<+% database_Strain_Family +
  geom_tippoint(aes(color = Family), size = 2) +
  geom_tiplab(align=TRUE, linetype='dashed', linesize=.3, size = 3, offset = 0.1) +
  geom_treescale(x=0.7, y=-1.9, fontsize=3, linesize=1, offset=1)+
  geom_balance(node=204, fill='grey80', alpha=0.6, extendto=1)+
  geom_balance(node=155, fill='grey80', alpha=0.6, extendto=1)+
  geom_balance(node=225, fill='grey10', alpha=0.6, extendto=1)+
  geom_balance(node=247, fill='grey40', alpha=0.6, extendto=1)+
  # geom_text(aes(label=node), hjust=-.3) +
  scale_color_manual(values = database_level_cols_Family)

tree_family_branch_line
```

# Abundance of isolates in microbiome
Abundance of isolates from strain collection in microbiome datasets of the field & greenhouse
Form quantitative values to quantitative. 
Abundant strains are defined as abundance > 0.1. 

```{r, warning=FALSE, include=FALSE}
tree_data <- tree_data %>%
  mutate(Greenhouse_B73_feedback_abundant = case_when(Greenhouse_B73_feedback > 0.1 ~ TRUE,
                              Greenhouse_B73_feedback < 0.1 ~ FALSE)) %>%
  mutate(Changins_B73_field_abundant = case_when(Changins_B73_field > 0.1 ~ TRUE,
                              Changins_B73_field < 0.1 ~ FALSE)) %>%
  mutate(Zurich_W22_field_abundant = case_when(Zurich_W22_field > 0.1 ~ TRUE,
                              Zurich_W22_field < 0.1 ~ FALSE)) %>%
  mutate(Zurich_B73_field_abundant = case_when(Zurich_B73_field  > 0.1 ~ TRUE,
                              Zurich_B73_field  < 0.1 ~ FALSE)) %>%
  mutate(Ithaca_W22_field_abundant = case_when(Ithaca_W22_field  > 0.1 ~ TRUE,
                              Ithaca_W22_field  < 0.1 ~ FALSE)) %>%
  mutate(Sheffield_W22_field_abundant = case_when(Sheffield_W22_field > 0.1 ~ TRUE,
                              Sheffield_W22_field < 0.1 ~ FALSE))
```

```{r, warning=FALSE, include=FALSE}
# List of strains in the phylogenetic tree
strains <- Tree_16s_unique$tip.label %>% unique()
strains %>% length()

# Filter for the abundant strains
tree_data_abundant <- tree_data %>% filter(Strain %in% strains) %>%
                      dplyr::select(Greenhouse_B73_feedback_abundant, Changins_B73_field_abundant,
                                    Zurich_W22_field_abundant, Zurich_B73_field_abundant,
                                    Ithaca_W22_field_abundant, Sheffield_W22_field_abundant) 

tree_data_strains_MRB <- tree_data %>% filter(Strain %in% strains)

strains_abundant_fields <- 
  cbind(tree_data_strains_MRB %>% 
        dplyr::count(Greenhouse_B73_feedback_abundant) %>%
        filter(Greenhouse_B73_feedback_abundant %in% TRUE),
        tree_data_strains_MRB %>% 
          dplyr::count(Changins_B73_field_abundant) %>% 
          filter(Changins_B73_field_abundant %in% TRUE),
        tree_data_strains_MRB %>% 
          dplyr::count(Zurich_W22_field_abundant) %>% 
          filter(Zurich_W22_field_abundant %in% TRUE),
        tree_data_strains_MRB %>% 
          dplyr::count(Zurich_B73_field_abundant) %>% 
          filter(Zurich_B73_field_abundant %in% TRUE),
        tree_data_strains_MRB %>% 
          dplyr::count(Ithaca_W22_field_abundant) %>% 
          filter(Ithaca_W22_field_abundant %in% TRUE),
        tree_data_strains_MRB %>% 
          dplyr::count(Sheffield_W22_field_abundant) %>% 
          filter(Sheffield_W22_field_abundant %in% TRUE))

colnames(strains_abundant_fields) <- c("Greenhouse_B73_feedback_abundant", "Greenhouse_B73",
                                     "Changins_B73_field_abundant", "Changins_B73", 
                                     "Zurich_W22_field_abundant", "Zurich_W22",    
                                     "Zurich_B73_field_abundant", "Zurich_B73",   
                                     "Ithaca_W22_field_abundant",   "Ithaca_W22",
                                     "Sheffield_W22_field_abundant",  "Sheffield_W22")

strains_abundant_fields %<>% dplyr::select(Greenhouse_B73, Changins_B73, Zurich_W22, Zurich_B73, Ithaca_W22, Sheffield_W22) %>% mutate(strains_total = "151")
strains_abundant_fields %>% knitr::kable()

# 151 strains in total

strains_abundant_fields %<>% t() %>% as.data.frame() %>% dplyr::rename(isolates = V1) %>% dplyr::slice(-7) %>% mutate(location = rownames(.)) %>% mutate(isolates_total = "151")
```

Amount of strains mapping to the abundant microbiome members at various locations.
```{r, warning = FALSE, error = FALSE, echo=FALSE, message=FALSE, fig.width=10, fig.height=7.5}
mapped_strains_counts <- strains_abundant_fields %>% 
  filter(!location %in% "Zurich_W22") %>% 
  mutate(location = factor(location, levels = c("Greenhouse_B73", "Changins_B73", "Zurich_B73", "Ithaca_W22",  "Sheffield_W22"))) %>% 
  mutate(isolates = as.numeric(isolates)) %>% 
  mutate(isolates_total = as.numeric(isolates_total)) %>% 
  mutate(isolates_not_mapped = isolates_total-isolates) %>% 
  dplyr::select(location, isolates, isolates_not_mapped) %>% 
  pivot_longer(cols = c(2,3)) %>% 
  mutate(name = factor(name, levels = c("isolates_not_mapped", "isolates"))) %>% 
  mutate(count = c("112", NA, "139", NA, "117", NA, "140", NA, "84", NA))

mapped_strains_counts_plot <- mapped_strains_counts %>% 
  ggplot(aes(x = location, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", show.legend = TRUE) +
  geom_text(aes(label = count), y = 10)+
  theme_classic() +
  scale_y_continuous(expand = expansion(mult = c(0, NA)))+
  theme(axis.text.x=element_text(angle = -90, hjust = 0, vjust = 0.5)) +
  scale_x_discrete(labels= c("Changins pot", "Changins field", "Reckenholz field", "Aurora field", "Sheffield pot"))+
  scale_fill_manual(values = c("grey", "khaki4"), labels = c("isolates not mapped", "isolates mapped"))+
  labs(x = "", 
       fill = "", 
       y = "MRB isolates")

mapped_strains_counts_plot

# # ggsave(plot = mapped_strains_counts_plot,  filename = "mapped_strains_counts_plot.pdf", width = 10, height = 12, dpi = 300, scale = 1, units = "cm")
# 
# # ggsave(plot = mapped_strains_counts_plot, filename = "mapped_strains_counts_plot.svg", width = 10, height = 12, dpi = 300, scale = 1, units = "cm")

```

# Tree with mapping
The tree is annotated with the quantitative abundance data from mapping greenhouse root microbiome dataset and qualitative information on the abundance in field microbiome datasets in the field (Changins, Zurich, Ithaca) and in the greenhouse (Sheffield). The outermost ring indicates the strains used in growth assays.
```{r, warning = FALSE, error = FALSE, echo=FALSE, message=FALSE, fig.width=20, fig.height=15}
p_ChFB_ASV <- gheatmap(tree_family_branch_line + new_scale_fill(),
         tree_data %>% 
         filter(Greenhouse_B73_feedback  > 0) %>% 
         dplyr::select(Strain, Greenhouse_B73_feedback ) %>% 
         dplyr::rename(WT_GH = Greenhouse_B73_feedback ) %>% 
         distinct() %>% na.omit() %>% 
         as.data.frame() %>% column_to_rownames("Strain") ,
         offset=0.3, 
         width=.07,
         colnames = FALSE)  +
         scale_fill_gradient2(low = "linen", mid = "gold", high ="coral4", midpoint = 3, 
                              na.value = "white", name="Abundance roots")

p_Ch <- gheatmap(p_ChFB_ASV + new_scale_fill(),
         tree_data %>% 
         dplyr::select(Strain, Changins_B73_field_abundant) %>% 
         dplyr::rename(Ch_B73 = Changins_B73_field_abundant) %>% 
         distinct() %>% na.omit() %>% 
         as.data.frame() %>% column_to_rownames("Strain") ,
         offset=0.42, 
         width=.02,
         colnames = FALSE)  +
         scale_fill_manual(values = c("white", "grey40"), guide = "none")

p_ZhB73 <- gheatmap(p_Ch + new_scale_fill(),
         tree_data %>% 
         dplyr::select(Strain, Zurich_B73_field_abundant) %>% 
         dplyr::rename(Zh_B73 = Zurich_B73_field_abundant) %>% 
         distinct() %>% na.omit() %>% 
         as.data.frame() %>% column_to_rownames("Strain") ,
         offset=0.44, 
         width=.02,
         colnames = FALSE)  +
         scale_fill_manual(values = c("white", "grey40"), guide = "none")

p_AuW22 <- gheatmap(p_ZhB73 + new_scale_fill(),
         tree_data %>% 
         dplyr::select(Strain, Ithaca_W22_field_abundant ) %>% 
         dplyr::rename(Au_W22 = Ithaca_W22_field_abundant ) %>% 
         distinct() %>% na.omit() %>% 
         as.data.frame() %>% column_to_rownames("Strain") ,
         offset=0.46, 
         width=.02,
         colnames = FALSE)  +
        scale_fill_manual(values = c("white", "grey40"), guide = "none")

p_ShW22 <- gheatmap(p_AuW22 + new_scale_fill(),
         tree_data %>% 
         dplyr::select(Strain, Sheffield_W22_field_abundant) %>% 
         dplyr::rename(Sh_W22 = Sheffield_W22_field_abundant) %>% 
         distinct() %>% na.omit() %>% 
         as.data.frame() %>% column_to_rownames("Strain") ,
         offset=0.48, width=.02,
         colnames = FALSE)  +
         scale_fill_manual(values = c("white", "grey40"), guide = "none")

p_tol <- gheatmap(p_ShW22 + new_scale_fill(),
         tree_data %>% 
         dplyr::select(Strain, tolerance_test) %>% 
           filter(tolerance_test %in% "TRUE") %>% 
         distinct() %>% 
         as.data.frame() %>% column_to_rownames("Strain") ,
         offset=0.55, width=.02,
         colnames = FALSE)  +
         scale_fill_manual(values ="black", na.value = "white", guide = "none")

all_MRB_branch_line <- p_tol

all_MRB_branch_line
# 
# ggplot2::ggsave(plot = all_MRB_branch_line,  filename = "all_MRB_branch_line.pdf", width = 60, height = 34, dpi = 300, scale = 1, units = "cm")
# 
# ggplot2::ggsave(plot = all_MRB_branch_line,  filename = "all_MRB_branch_line.svg", width = 60, height = 34, dpi = 300, scale = 1, units = "cm")
```

```{r}
sessionInfo()
```


